---
title: "Investigate PROs and cytokine levels in CARTcell MM patients"
author: "Christelle Colin-Leitzinger"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: united
    highlight: pygments
    df_print: kable
editor_options: 
  chunk_output_type: console
---

<style type="text/css">

.figure {
    margin-top: 100px;
    margin-bottom: 100px;
}

table {
    margin-top: 10px;
    margin-bottom: 25px !important;
}

th, td { padding: 5px; }

</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
```

```{r library}
library(tidyverse)
library(gtsummary)
library(labelled)
library(survminer)
library(survival)
theme_set(theme_classic(base_size = 18))
theme_gtsummary_compact()
```

```{r load data}
pros_cytokines_data <- 
  read_rds(paste0(here::here(), "/pros_cytokines_data.rds"))

pros_data <- pros_cytokines_data %>% 
  filter(data_has_pros == "Yes")
cyto_data <- pros_cytokines_data %>% 
  filter(data_has_cytokines == "Yes")
```

# Total PROs dataset (n = `r nrow(pros_data)`)
What are the unknowns?
```{r}
pros_data %>% 
    select(gr2_CRS, gr2_ICANS,
           promis_anxiety_tscore_baseline,
           promis_depression_tscore_baseline,
           promis_social_tscore_baseline) %>%
    tbl_summary() %>%
    bold_labels()
```

## Categories
### Toxicities and responses
```{r, results = 'asis'}
table_var <- c("gr2_CRS", "CRS_any",
               "gr2_ICANS", "ICANS_any",
         # "day30response_v2", 
         "ORR_30days", "CRorbetter_30days",
         # "mon3response_v2", 
         "ORR_3mon", "CRorbetter_3mon",
         "best_ORR", "best_CRorbetter"
)

for (i in table_var){
  
  tbl <- pros_data %>% 
    select(i, 
           promis_anxiety_tscore_baseline,
           promis_depression_tscore_baseline,
           promis_social_tscore_baseline) %>%
    tbl_summary(by = i) %>%
    bold_labels() %>%
    add_p() %>% bold_p(t= 0.05) %>%
    modify_spanning_header(everything() ~ paste(i))
  print(tbl)
  
}
```

### day 90 PROs
```{r, results = 'asis'}
table_var <- c("factg_total_90_cat", 
         # "ti_90_cat", "ti_90_cat2", 
         "ti_90_cat3",
         "promis_fatigue_tscore_90_cat",
         "promis_fatigue_tscore_90_cat2",
         "promis_fatigue_tscore_90_cat3",
         "promis_pain_tscore_90_cat",
         "promis_pain_tscore_90_cat2",
         "promis_pain_tscore_90_cat3",
         "promis_physical_tscore_90_cat",
         "promis_physical_tscore_90_cat2",
         "promis_physical_tscore_90_cat3"
)

for (i in table_var){
  
  tbl <- pros_data %>% 
    select(i, 
           promis_anxiety_tscore_baseline,
           promis_depression_tscore_baseline,
           promis_social_tscore_baseline) %>%
    tbl_summary(by = i) %>%
    bold_labels() %>%
    add_p() %>% bold_p(t= 0.05) %>%
    modify_spanning_header(everything() ~ paste(i))
  print(tbl)
  
}
```

## Continuous
### Anxiety
```{r}
summary(lm(factg_total_90 ~ promis_anxiety_tscore_baseline, data = pros_data))

summary(lm(ti_90 ~ promis_anxiety_tscore_baseline, data = pros_data))

summary(lm(promis_fatigue_tscore_90 ~ promis_anxiety_tscore_baseline, data = pros_data))

summary(lm(promis_pain_tscore_90 ~ promis_anxiety_tscore_baseline, data = pros_data))

summary(lm(promis_physical_tscore_90 ~ promis_anxiety_tscore_baseline, data = pros_data))
```

### Depression 
```{r}
summary(lm(factg_total_90 ~ promis_depression_tscore_baseline, data = pros_data))

summary(lm(ti_90 ~ promis_depression_tscore_baseline, data = pros_data))

summary(lm(promis_fatigue_tscore_90 ~ promis_depression_tscore_baseline, data = pros_data))

summary(lm(promis_pain_tscore_90 ~ promis_depression_tscore_baseline, data = pros_data))

summary(lm(promis_physical_tscore_90 ~ promis_depression_tscore_baseline, data = pros_data))
```

### Social 
```{r}
summary(lm(factg_total_90 ~ promis_social_tscore_baseline, data = pros_data))

summary(lm(ti_90 ~ promis_social_tscore_baseline, data = pros_data))

summary(lm(promis_fatigue_tscore_90 ~ promis_social_tscore_baseline, data = pros_data))

summary(lm(promis_pain_tscore_90 ~ promis_social_tscore_baseline, data = pros_data))

summary(lm(promis_physical_tscore_90 ~ promis_social_tscore_baseline, data = pros_data))
```

## Survival
### 1.HR OS
```{r}
tbl_uni <- pros_data %>% 
  select(os_event, mo_os_from_infusion,
         promis_anxiety_tscore_baseline,
         promis_depression_tscore_baseline,
         promis_social_tscore_baseline,
         promis_anxiety_tscore_baseline_cat,
         promis_anxiety_tscore_baseline_cat2,
         promis_anxiety_tscore_baseline_cat3,
         promis_depression_tscore_baseline_cat,
         promis_depression_tscore_baseline_cat2,
         promis_depression_tscore_baseline_cat3,
         promis_social_tscore_baseline_cat,
         promis_social_tscore_baseline_cat2,
         promis_social_tscore_baseline_cat3
         ) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = pros_data$mo_os_from_infusion,
                             event = pros_data$os_event)),
                   exponentiate = TRUE) %>%
  bold_labels() %>% italicize_levels() %>%
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_uni
```

### 1.HR PFS
```{r}
tbl_uni <- pros_data %>% 
  select(pfs_event, mo_pfs_from_infusion,
         promis_anxiety_tscore_baseline,
         promis_depression_tscore_baseline,
         promis_social_tscore_baseline,
         promis_anxiety_tscore_baseline_cat,
         promis_anxiety_tscore_baseline_cat2,
         promis_anxiety_tscore_baseline_cat3,
         promis_depression_tscore_baseline_cat,
         promis_depression_tscore_baseline_cat2,
         promis_depression_tscore_baseline_cat3,
         promis_social_tscore_baseline_cat,
         promis_social_tscore_baseline_cat2,
         promis_social_tscore_baseline_cat3
         ) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = pros_data$mo_pfs_from_infusion,
                             event = pros_data$pfs_event)),
                   exponentiate = TRUE) %>%
  bold_labels() %>% italicize_levels() %>%
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_uni
```

# Total Cytokine dataset (n = `r nrow(cyto_data)`)
What are the unknowns?
```{r}
cyto_data %>% 
  tbl_cross(row = baseline_ferritin_cat, col = data_has_cytokines)
pros_cytokines_data %>% 
  tbl_cross(row = baseline_ferritin_cat, col = data_has_cytokines)
pros_cytokines_data %>% 
    select(gr2_CRS, gr2_ICANS, 
           baseline_ferritin_cat, baseline_ferritin,
           peak_ferritin,
           baseline_crp_cat, baseline_crp,
           peak_crp,
           IL2_baseline, peak_il2,
           IL6_baseline, peak_il6,
           IFNg_baseline, peak_ifng,
           TNFa_baseline, peak_tnfa) %>%
    tbl_summary() %>%
    bold_labels()
```

## Categories
### toxicities and responses
```{r, results = 'asis'}
table_var <- c("gr2_CRS", "CRS_any",
               "gr2_ICANS", "ICANS_any",
         # "day30response_v2", 
         "ORR_30days", "CRorbetter_30days",
         # "mon3response_v2", 
         "ORR_3mon", "CRorbetter_3mon",
         "best_ORR", "best_CRorbetter"
)

for (i in table_var){
  
  tbl <- pros_cytokines_data %>% 
    select(i, 
           baseline_ferritin_cat, baseline_ferritin,
           peak_ferritin,
           baseline_crp_cat, baseline_crp,
           peak_crp,
           IL2_baseline, peak_il2,
           IL6_baseline, peak_il6,
           IFNg_baseline, peak_ifng,
           TNFa_baseline, peak_tnfa) %>%
    tbl_summary(by = i) %>%
    bold_labels() %>%
    add_p() %>% bold_p(t= 0.05) %>%
    modify_spanning_header(everything() ~ paste(i))
  print(tbl)
  
}
```

### day 90 PROs
```{r, results = 'asis'}
table_var <- c("factg_total_90_cat", 
         # "ti_90_cat", "ti_90_cat2", 
         "ti_90_cat3",
         "promis_fatigue_tscore_90_cat",
         "promis_fatigue_tscore_90_cat2",
         "promis_fatigue_tscore_90_cat3",
         "promis_pain_tscore_90_cat",
         "promis_pain_tscore_90_cat2",
         "promis_pain_tscore_90_cat3",
         "promis_physical_tscore_90_cat",
         "promis_physical_tscore_90_cat2",
         "promis_physical_tscore_90_cat3"
)

for (i in table_var){
  
  tbl <- pros_cytokines_data %>% 
    select(i, 
           baseline_ferritin_cat, baseline_ferritin,
           peak_ferritin,
           baseline_crp_cat, baseline_crp,
           peak_crp,
           IL2_baseline, peak_il2,
           IL6_baseline, peak_il6,
           IFNg_baseline, peak_ifng,
           TNFa_baseline, peak_tnfa) %>%
    tbl_summary(by = i) %>%
    bold_labels() %>%
    add_p() %>% bold_p(t= 0.05) %>%
    modify_spanning_header(everything() ~ paste(i))
  print(tbl)
  
}
```

## Continuous

### factg_total_90
```{r}
summary(lm(factg_total_90 ~ baseline_ferritin, data = pros_cytokines_data))
summary(lm(factg_total_90 ~ baseline_ferritin_cat, data = pros_cytokines_data))
summary(lm(factg_total_90 ~ max_ferritin, data = pros_cytokines_data))
summary(lm(factg_total_90 ~ peak_ferritin, data = pros_cytokines_data))
summary(lm(factg_total_90 ~ baseline_crp, data = pros_cytokines_data))
summary(lm(factg_total_90 ~ baseline_crp_cat, data = pros_cytokines_data))
summary(lm(factg_total_90 ~ max_crp, data = pros_cytokines_data))
print("zero normal peak_crp with pros data")
# summary(lm(factg_total_90 ~ peak_crp, data = pros_cytokines_data))
# pros_cytokines_data %>% 
#   select(factg_total_90, baseline_ferritin) %>% 
#   tbl_uvregression(method = lm,
#                    y = factg_total_90)
summary(lm(factg_total_90 ~ IL2_baseline, data = pros_cytokines_data))
summary(lm(factg_total_90 ~ peak_il2, data = pros_cytokines_data))
summary(lm(factg_total_90 ~ IL6_baseline, data = pros_cytokines_data))
summary(lm(factg_total_90 ~ peak_il6, data = pros_cytokines_data))
summary(lm(factg_total_90 ~ IFNg_baseline, data = pros_cytokines_data))
summary(lm(factg_total_90 ~ peak_ifng, data = pros_cytokines_data))
summary(lm(factg_total_90 ~ TNFa_baseline, data = pros_cytokines_data))
summary(lm(factg_total_90 ~ peak_tnfa, data = pros_cytokines_data))
```

### ti_90
```{r}
summary(lm(ti_90 ~ baseline_ferritin, data = pros_cytokines_data))
summary(lm(ti_90 ~ baseline_ferritin_cat, data = pros_cytokines_data))
summary(lm(ti_90 ~ max_ferritin, data = pros_cytokines_data))
summary(lm(ti_90 ~ peak_ferritin, data = pros_cytokines_data))
summary(lm(ti_90 ~ baseline_crp, data = pros_cytokines_data))
summary(lm(ti_90 ~ baseline_crp_cat, data = pros_cytokines_data))
summary(lm(ti_90 ~ max_crp, data = pros_cytokines_data))
print("zero normal peak_crp with pros data")
# summary(lm(ti_90 ~ peak_crp, data = pros_cytokines_data))
summary(lm(ti_90 ~ IL2_baseline, data = pros_cytokines_data))
summary(lm(ti_90 ~ peak_il2, data = pros_cytokines_data))
summary(lm(ti_90 ~ IL6_baseline, data = pros_cytokines_data))
summary(lm(ti_90 ~ peak_il6, data = pros_cytokines_data))
summary(lm(ti_90 ~ IFNg_baseline, data = pros_cytokines_data))
summary(lm(ti_90 ~ peak_ifng, data = pros_cytokines_data))
summary(lm(ti_90 ~ TNFa_baseline, data = pros_cytokines_data))
summary(lm(ti_90 ~ peak_tnfa, data = pros_cytokines_data))
```

### promis_fatigue_tscore_90
```{r}
summary(lm(promis_fatigue_tscore_90 ~ baseline_ferritin, data = pros_cytokines_data))
summary(lm(promis_fatigue_tscore_90 ~ baseline_ferritin_cat, data = pros_cytokines_data))
summary(lm(promis_fatigue_tscore_90 ~ max_ferritin, data = pros_cytokines_data))
summary(lm(promis_fatigue_tscore_90 ~ peak_ferritin, data = pros_cytokines_data))
summary(lm(promis_fatigue_tscore_90 ~ baseline_crp, data = pros_cytokines_data))
summary(lm(promis_fatigue_tscore_90 ~ baseline_crp_cat, data = pros_cytokines_data))
summary(lm(promis_fatigue_tscore_90 ~ max_crp, data = pros_cytokines_data))
print("zero normal peak_crp with pros data")
# summary(lm(promis_fatigue_tscore_90 ~ peak_crp, data = pros_cytokines_data))
summary(lm(promis_fatigue_tscore_90 ~ IL2_baseline, data = pros_cytokines_data))
summary(lm(promis_fatigue_tscore_90 ~ peak_il2, data = pros_cytokines_data))
summary(lm(promis_fatigue_tscore_90 ~ IL6_baseline, data = pros_cytokines_data))
summary(lm(promis_fatigue_tscore_90 ~ peak_il6, data = pros_cytokines_data))
summary(lm(promis_fatigue_tscore_90 ~ IFNg_baseline, data = pros_cytokines_data))
summary(lm(promis_fatigue_tscore_90 ~ peak_ifng, data = pros_cytokines_data))
summary(lm(promis_fatigue_tscore_90 ~ TNFa_baseline, data = pros_cytokines_data))
summary(lm(promis_fatigue_tscore_90 ~ peak_tnfa, data = pros_cytokines_data))
```

### promis_pain_tscore_90
```{r}
summary(lm(promis_pain_tscore_90 ~ baseline_ferritin, data = pros_cytokines_data))
summary(lm(promis_pain_tscore_90 ~ baseline_ferritin_cat, data = pros_cytokines_data))
summary(lm(promis_pain_tscore_90 ~ max_ferritin, data = pros_cytokines_data))
summary(lm(promis_pain_tscore_90 ~ peak_ferritin, data = pros_cytokines_data))
summary(lm(promis_pain_tscore_90 ~ baseline_crp, data = pros_cytokines_data))
summary(lm(promis_pain_tscore_90 ~ baseline_crp_cat, data = pros_cytokines_data))
summary(lm(promis_pain_tscore_90 ~ max_crp, data = pros_cytokines_data))
print("zero normal peak_crp with pros data")
# summary(lm(promis_pain_tscore_90 ~ peak_crp, data = pros_cytokines_data))
summary(lm(promis_pain_tscore_90 ~ IL2_baseline, data = pros_cytokines_data))
summary(lm(promis_pain_tscore_90 ~ peak_il2, data = pros_cytokines_data))
summary(lm(promis_pain_tscore_90 ~ IL6_baseline, data = pros_cytokines_data))
summary(lm(promis_pain_tscore_90 ~ peak_il6, data = pros_cytokines_data))
summary(lm(promis_pain_tscore_90 ~ IFNg_baseline, data = pros_cytokines_data))
summary(lm(promis_pain_tscore_90 ~ peak_ifng, data = pros_cytokines_data))
summary(lm(promis_pain_tscore_90 ~ TNFa_baseline, data = pros_cytokines_data))
summary(lm(promis_pain_tscore_90 ~ peak_tnfa, data = pros_cytokines_data))
```

### promis_physical_tscore_90
```{r}
summary(lm(promis_physical_tscore_90 ~ baseline_ferritin, data = pros_cytokines_data))
summary(lm(promis_physical_tscore_90 ~ baseline_ferritin_cat, data = pros_cytokines_data))
summary(lm(promis_physical_tscore_90 ~ max_ferritin, data = pros_cytokines_data))
summary(lm(promis_physical_tscore_90 ~ peak_ferritin, data = pros_cytokines_data))
summary(lm(promis_physical_tscore_90 ~ baseline_crp, data = pros_cytokines_data))
summary(lm(promis_physical_tscore_90 ~ baseline_crp_cat, data = pros_cytokines_data))
summary(lm(promis_physical_tscore_90 ~ max_crp, data = pros_cytokines_data))
print("zero normal peak_crp with pros data")
# summary(lm(promis_physical_tscore_90 ~ peak_crp, data = pros_cytokines_data))
summary(lm(promis_physical_tscore_90 ~ IL2_baseline, data = pros_cytokines_data))
summary(lm(promis_physical_tscore_90 ~ peak_il2, data = pros_cytokines_data))
summary(lm(promis_physical_tscore_90 ~ IL6_baseline, data = pros_cytokines_data))
summary(lm(promis_physical_tscore_90 ~ peak_il6, data = pros_cytokines_data))
summary(lm(promis_physical_tscore_90 ~ IFNg_baseline, data = pros_cytokines_data))
summary(lm(promis_physical_tscore_90 ~ peak_ifng, data = pros_cytokines_data))
summary(lm(promis_physical_tscore_90 ~ TNFa_baseline, data = pros_cytokines_data))
summary(lm(promis_physical_tscore_90 ~ peak_tnfa, data = pros_cytokines_data))
```

```{r}
# a <- pros_cytokines_data %>% 
#   # mutate_at(c("baseline_ferritin_cat",
#   #             "peak_ferritin",
#   #             "baseline_crp_cat",
#   #             "peak_crp"), ~ case_when(
#   #   str_detect(., "Normal")    ~ 0,
#   #   str_detect(., "≥ ULN at LD")   ~ 1
#   # )) %>% 
#   mutate_at(c("factg_total_90_cat"#,
#               # "peak_ferritin",
#               # "baseline_crp_cat"
#               ), ~ case_when(
#     str_detect(., "Low")    ~ 0,
#     str_detect(., "Normal")   ~ 1
#   ))
```
<!-- ### Baseline ferritin -->
```{r}
# glm(factg_total_90_cat ~ baseline_ferritin_cat,
#     data = a,
#     family = "binomial") %>%
#   tbl_regression(exponentiate = TRUE, 
#                  intercept = TRUE) %>%
#   add_nevent(location = "level") %>% add_n(location = "level") %>%
#   modify_spanning_header(everything() ~ "**factg_total_90_cat 0 is Low, 1 is Normal**") %>%
#   bold_p(t = .05) 
```






<!-- ```{r} -->
<!-- glm(baseline_ferritin_cat ~ factg_total_90, -->
<!--     data = a, -->
<!--     family = "binomial") %>% -->
<!--   tbl_regression(exponentiate = TRUE,  -->
<!--                  intercept = TRUE) %>% -->
<!--   add_nevent(location = "level") %>% add_n(location = "level") %>% -->
<!--   modify_spanning_header(everything() ~ "**baseline_ferritin 0 is normal 1 is ≥ ULN at LD (≥ 400)**") %>% -->
<!--   bold_p(t = .05)  -->

<!-- glm(baseline_ferritin_cat ~ ti_90, -->
<!--     data = a, -->
<!--     family = "binomial") %>% -->
<!--   tbl_regression(exponentiate = TRUE,  -->
<!--                  intercept = TRUE) %>% -->
<!--   add_nevent(location = "level") %>% add_n(location = "level") %>% -->
<!--   modify_spanning_header(everything() ~ "**baseline_ferritin 0 is normal 1 is ≥ ULN at LD (≥ 400)**") %>% -->
<!--   bold_p(t = .05)  -->

<!-- glm(baseline_ferritin_cat ~ promis_fatigue_tscore_90, -->
<!--     data = a, -->
<!--     family = "binomial") %>% -->
<!--   tbl_regression(exponentiate = TRUE,  -->
<!--                  intercept = TRUE) %>% -->
<!--   add_nevent(location = "level") %>% add_n(location = "level") %>% -->
<!--   modify_spanning_header(everything() ~ "**baseline_ferritin 0 is normal 1 is ≥ ULN at LD (≥ 400)**") %>% -->
<!--   bold_p(t = .05)  -->

<!-- glm(baseline_ferritin_cat ~ promis_pain_tscore_90, -->
<!--     data = a, -->
<!--     family = "binomial") %>% -->
<!--   tbl_regression(exponentiate = TRUE,  -->
<!--                  intercept = TRUE) %>% -->
<!--   add_nevent(location = "level") %>% add_n(location = "level") %>% -->
<!--   modify_spanning_header(everything() ~ "**baseline_ferritin 0 is normal 1 is ≥ ULN at LD (≥ 400)**") %>% -->
<!--   bold_p(t = .05)  -->

<!-- glm(baseline_ferritin_cat ~ promis_physical_tscore_90, -->
<!--     data = a, -->
<!--     family = "binomial") %>% -->
<!--   tbl_regression(exponentiate = TRUE,  -->
<!--                  intercept = TRUE) %>% -->
<!--   add_nevent(location = "level") %>% add_n(location = "level") %>% -->
<!--   modify_spanning_header(everything() ~ "**baseline_ferritin 0 is normal 1 is ≥ ULN at LD (≥ 400)**") %>% -->
<!--   bold_p(t = .05)  -->
<!-- ``` -->

<!-- ### Peak ferritin -->
<!-- ```{r} -->
<!-- glm(peak_ferritin ~ factg_total_90, -->
<!--     data = a, -->
<!--     family = "binomial") %>% -->
<!--   tbl_regression(exponentiate = TRUE,  -->
<!--                  intercept = TRUE) %>% -->
<!--   add_nevent(location = "level") %>% add_n(location = "level") %>% -->
<!--   modify_spanning_header(everything() ~ "**peak_ferritin 0 is normal, 1 is ≥ ULN at LD**") %>% -->
<!--   bold_p(t = .05)  -->

<!-- glm(peak_ferritin ~ ti_90, -->
<!--     data = a, -->
<!--     family = "binomial") %>% -->
<!--   tbl_regression(exponentiate = TRUE,  -->
<!--                  intercept = TRUE) %>% -->
<!--   add_nevent(location = "level") %>% add_n(location = "level") %>% -->
<!--   modify_spanning_header(everything() ~ "**peak_ferritin 0 is normal, 1 is ≥ ULN at LD**") %>% -->
<!--   bold_p(t = .05)  -->

<!-- glm(peak_ferritin ~ promis_fatigue_tscore_90, -->
<!--     data = a, -->
<!--     family = "binomial") %>% -->
<!--   tbl_regression(exponentiate = TRUE,  -->
<!--                  intercept = TRUE) %>% -->
<!--   add_nevent(location = "level") %>% add_n(location = "level") %>% -->
<!--   modify_spanning_header(everything() ~ "**peak_ferritin 0 is normal, 1 is ≥ ULN at LD**") %>% -->
<!--   bold_p(t = .05)  -->

<!-- glm(peak_ferritin ~ promis_pain_tscore_90, -->
<!--     data = a, -->
<!--     family = "binomial") %>% -->
<!--   tbl_regression(exponentiate = TRUE,  -->
<!--                  intercept = TRUE) %>% -->
<!--   add_nevent(location = "level") %>% add_n(location = "level") %>% -->
<!--   modify_spanning_header(everything() ~ "**peak_ferritin 0 is normal, 1 is ≥ ULN at LD**") %>% -->
<!--   bold_p(t = .05)  -->

<!-- glm(peak_ferritin ~ promis_physical_tscore_90, -->
<!--     data = a, -->
<!--     family = "binomial") %>% -->
<!--   tbl_regression(exponentiate = TRUE,  -->
<!--                  intercept = TRUE) %>% -->
<!--   add_nevent(location = "level") %>% add_n(location = "level") %>% -->
<!--   modify_spanning_header(everything() ~ "**peak_ferritin 0 is normal, 1 is ≥ ULN at LD**") %>% -->
<!--   bold_p(t = .05)  -->
<!-- ``` -->

<!-- ### Baseline CRP -->
<!-- ```{r} -->
<!-- glm(baseline_crp_cat ~ factg_total_90, -->
<!--     data = a, -->
<!--     family = "binomial") %>% -->
<!--   tbl_regression(exponentiate = TRUE,  -->
<!--                  intercept = TRUE) %>% -->
<!--   add_nevent(location = "level") %>% add_n(location = "level") %>% -->
<!--   modify_spanning_header(everything() ~ "**baseline_crp 0 is normal, 1 is ≥ ULN at LD**") %>% -->
<!--   bold_p(t = .05)  -->

<!-- glm(baseline_crp_cat ~ ti_90, -->
<!--     data = a, -->
<!--     family = "binomial") %>% -->
<!--   tbl_regression(exponentiate = TRUE,  -->
<!--                  intercept = TRUE) %>% -->
<!--   add_nevent(location = "level") %>% add_n(location = "level") %>% -->
<!--   modify_spanning_header(everything() ~ "**baseline_crp 0 is normal, 1 is ≥ ULN at LD**") %>% -->
<!--   bold_p(t = .05)  -->

<!-- glm(baseline_crp_cat ~ promis_fatigue_tscore_90, -->
<!--     data = a, -->
<!--     family = "binomial") %>% -->
<!--   tbl_regression(exponentiate = TRUE,  -->
<!--                  intercept = TRUE) %>% -->
<!--   add_nevent(location = "level") %>% add_n(location = "level") %>% -->
<!--   modify_spanning_header(everything() ~ "**baseline_crp 0 is normal, 1 is ≥ ULN at LD**") %>% -->
<!--   bold_p(t = .05)  -->

<!-- glm(baseline_crp_cat ~ promis_pain_tscore_90, -->
<!--     data = a, -->
<!--     family = "binomial") %>% -->
<!--   tbl_regression(exponentiate = TRUE,  -->
<!--                  intercept = TRUE) %>% -->
<!--   add_nevent(location = "level") %>% add_n(location = "level") %>% -->
<!--   modify_spanning_header(everything() ~ "**baseline_crp 0 is normal, 1 is ≥ ULN at LD**") %>% -->
<!--   bold_p(t = .05)  -->

<!-- glm(baseline_crp_cat ~ promis_physical_tscore_90, -->
<!--     data = a, -->
<!--     family = "binomial") %>% -->
<!--   tbl_regression(exponentiate = TRUE,  -->
<!--                  intercept = TRUE) %>% -->
<!--   add_nevent(location = "level") %>% add_n(location = "level") %>% -->
<!--   modify_spanning_header(everything() ~ "**baseline_crp 0 is normal, 1 is ≥ ULN at LD**") %>% -->
<!--   bold_p(t = .05)  -->
<!-- ``` -->

<!-- ### Peak CRP -->
<!-- peak CRP has only 2 zero -->
<!-- ```{r} -->
<!-- glm(peak_crp ~ factg_total_90, -->
<!--     data = a, -->
<!--     family = "binomial") %>% -->
<!--   tbl_regression(exponentiate = TRUE, -->
<!--                  intercept = TRUE) %>% -->
<!--   add_nevent(location = "level") %>% add_n(location = "level") %>% -->
<!--   modify_spanning_header(everything() ~ "**peak_crp 0 is normal, 1 is ≥ ULN at LD**") %>% -->
<!--   bold_p(t = .05) -->

<!-- glm(peak_crp ~ ti_90, -->
<!--     data = a, -->
<!--     family = "binomial") %>% -->
<!--   tbl_regression(exponentiate = TRUE, -->
<!--                  intercept = TRUE) %>% -->
<!--   add_nevent(location = "level") %>% add_n(location = "level") %>% -->
<!--   modify_spanning_header(everything() ~ "**peak_crp 0 is normal, 1 is ≥ ULN at LD**") %>% -->
<!--   bold_p(t = .05) -->

<!-- glm(peak_crp ~ promis_fatigue_tscore_90, -->
<!--     data = a, -->
<!--     family = "binomial") %>% -->
<!--   tbl_regression(exponentiate = TRUE, -->
<!--                  intercept = TRUE) %>% -->
<!--   add_nevent(location = "level") %>% add_n(location = "level") %>% -->
<!--   modify_spanning_header(everything() ~ "**peak_crp 0 is normal, 1 is ≥ ULN at LD**") %>% -->
<!--   bold_p(t = .05) -->

<!-- glm(peak_crp ~ promis_pain_tscore_90, -->
<!--     data = a, -->
<!--     family = "binomial") %>% -->
<!--   tbl_regression(exponentiate = TRUE, -->
<!--                  intercept = TRUE) %>% -->
<!--   add_nevent(location = "level") %>% add_n(location = "level") %>% -->
<!--   modify_spanning_header(everything() ~ "**peak_crp 0 is normal, 1 is ≥ ULN at LD**") %>% -->
<!--   bold_p(t = .05) -->

<!-- glm(peak_crp ~ promis_physical_tscore_90, -->
<!--     data = a, -->
<!--     family = "binomial") %>% -->
<!--   tbl_regression(exponentiate = TRUE, -->
<!--                  intercept = TRUE) %>% -->
<!--   add_nevent(location = "level") %>% add_n(location = "level") %>% -->
<!--   modify_spanning_header(everything() ~ "**peak_crp 0 is normal, 1 is ≥ ULN at LD**") %>% -->
<!--   bold_p(t = .05) -->
<!-- ``` -->

<!-- ### Baseline IL2 -->

<!-- ### Peak IL2 -->

<!-- ### Baseline IL6 -->

<!-- ### Peak IL6 -->

<!-- ### Baseline IFNg -->

<!-- ### Peak IFNg -->

<!-- ### Baseline TNFa -->

<!-- ### Peak TNFa -->


